Figures

### 2019-05-13 figures/06_lulc_buffer_demo.Rmd
separate cdl and buffer analyses

```{r buffer-lulc_vs_iws-lulc, echo=FALSE, fig.height=3}
dt <- readRDS("../data/dt.rds") %>%
  mutate(diff = stream_cultivated_crops - ag_pct) %>%
  drop_na(diff)

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = diff > 3)) +
  geom_abline(aes(slope = 1, intercept = 0)) +
  theme(legend.position = 0)
```

```{r satellite, echo=FALSE}
# 
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
res_iws  <- query_gis("IWS", "lagoslakeid", 
                      dplyr::filter(dt, diff > 3)$lagoslakeid)

# ggplot() + 
#   geom_sf(data = state_sf()) +
#   geom_sf(data = res_pnt)

library(curl)
library(glue)
library(slippymath)
library(raster)
library(rgdal)

get_image <- function(outpath, iws){
  tile_grid <- bbox_to_tile_grid(st_bbox(
    st_transform(iws, 4326)), max_tiles = 15)

  mapbox_query_string <-
    paste0("https://api.mapbox.com/v4/mapbox.satellite/{zoom}/{x}/{y}.jpg90",
           "?access_token=",
           Sys.getenv("MAPBOX_API_KEY"))

  images <- apply(tile_grid$tiles, 1, function(i) {
    url     <- glue(mapbox_query_string, x = i[1], y = i[2], 
                zoom = tile_grid$zoom)
    outfile <- glue("../data/mapbox/{x}_{y}.jpg", x = i[1], y = i[2])
    get_if_not_exists(url, outfile)
    return(outfile)
  })

  raster_out <- compose_tile_grid(tile_grid, images)

  writeRaster(raster_out, outpath, options="INTERLEAVE=BAND")   
  return(raster_out)
}

outpaths     <- paste0("../data/mapbox/", res_iws$lagoslakeid, ".tif")
images       <- lapply(seq_along(outpaths), function(i) 
  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = res_iws[i,]))

iws_sized    <- which(abs(res_iws$IWSAreaHa - median(res_iws$IWSAreaHa)) < 1000)
images_sized <- images[iws_sized]

get_streams <- function(destfile){
  res <- lapply(iws_sized, function(x) 
            nhdR::nhd_plus_query(
              poly = res_iws[x,], dsn = "NHDFlowLine")$sp$NHDFlowLine)
  saveRDS(res, destfile)
  return(res)
}

res_streams <- get_if_not_exists(get_streams, "../data/nhd/res_streams.rds")

# m <- viewRGB(r) + 
#   mapview(res_streams[[1]]) + 
#   mapview(s, alpha.regions = 0, color = "red")
# 
# mapshot(m, file = paste0(getwd(), "/map.png"))
# extent(r); st_bbox(s)

i          <- 7
s          <- res_iws[iws_sized[i],]
r_raw      <- images_sized[[i]]
r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])

tab        <- as.data.frame(r, xy = TRUE)
names(tab) <- c("x", "y", "red", "green", "blue")
tab$red   <- scales::rescale(tab$red, to = c(0, 255))
tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
tab$green <- scales::rescale(tab$green, to = c(0, 255))
tab          <- tab[complete.cases(tab),]
tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)

ggplot() + 
  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[iws_sized[i],], alpha = 0, color = "red") +
  geom_sf(data = res_streams[[i]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void()

outpaths     <- paste0("../data/mapbox/", 6201, ".tif") # good sized but low stream ag
iws_temp     <- query_gis("IWS", "lagoslakeid", 6201)
# unlink("../data/mapbox/6201.tif")
images       <- lapply(seq_along(outpaths), function(i) 
  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = iws_temp))

get_streams <- function(destfile){
  res <- lapply(iws_sized, function(x) 
            nhdR::nhd_plus_query(
              poly = iws_temp, dsn = "NHDFlowLine")$sp$NHDFlowLine)
  saveRDS(res, destfile)
  return(res)
}

streams_temp <- get_if_not_exists(get_streams, "../data/nhd/temp_streams.rds")
r_raw      <- images[[1]]
r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])

tab        <- as.data.frame(r, xy = TRUE)
names(tab) <- c("x", "y", "red", "green", "blue")
tab$red   <- scales::rescale(tab$red, to = c(0, 255))
tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
tab$green <- scales::rescale(tab$green, to = c(0, 255))
tab          <- tab[complete.cases(tab),]
tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)

ggplot() + 
  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
  geom_sf(data = iws_temp, alpha = 0, color = "red") +
  geom_sf(data = streams_temp[[1]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void()

```{r cdl_viewport}
library(raster)
library(dplyr)

@@

test2 <- cdl_table %>% 
  dplyr::filter(description != "Background") %>%
  rename(n = Freq) %>%
  arrange(desc(n)) %>%
  group_by(category) %>%
  summarize(group_n = sum(n, na.rm = TRUE), is_ag = first(is_ag)) %>%
  ungroup() %>%
  mutate(percent = round((group_n / sum(group_n, na.rm = TRUE)) * 100, 0)) %>%
  dplyr::filter(percent >= 1) %>%
  arrange(is_ag, percent) 
%>%
  add_row(category = "ag", group_n = 100, is_ag = "ag", percent = 200)

test2 <- test2 %>%
  add_row(category = "ag", group_n = NA, is_ag = NA, percent = 
            sum(dplyr::filter(test2, is_ag == "ag" & 
                                category != "pasture")$percent))

ggplot() + 
  geom_col(data = test2, aes(x = category, 
                             y = percent, 
                             fill = category)) +
  theme(legend.direction = "horizontal", 
        legend.position = 0,
        axis.text.x = element_text(angle = 90)) +
  guides(fill = guide_legend(ncol = 2)) +
  ggtitle("CDL llid = 2745")
```

>>>>

```{r cdl_viewport, fig.height=5}
library(raster)
library(dplyr)
library(stars)

@@

test2 <- cdl_table %>% 
  dplyr::filter(description != "Background") %>%
  rename(n = Freq) %>%
  arrange(desc(n)) %>%
  group_by(category) %>%
  summarize(group_n = sum(n, na.rm = TRUE), is_ag = first(is_ag)) %>%
  ungroup() %>%
  mutate(percent = round((group_n / sum(group_n, na.rm = TRUE)) * 100, 0)) %>%
  dplyr::filter(percent >= 1) %>%
  arrange(is_ag, percent)

# test2 <- test2 %>%
#   add_row(category = "crops", group_n = NA, is_ag = NA, percent = 
#             sum(dplyr::filter(test2, is_ag == "ag" & 
#                                 category != "pasture")$percent))

g_bar <- ggplot() + 
  geom_col(data = test2, aes(x = category, 
                             y = percent, 
                             fill = category)) +
  theme(legend.direction = "horizontal", 
        legend.position = 0,
        axis.text.x = element_text(angle = 90)) +
  guides(fill = guide_legend(ncol = 2)) +
  ggtitle("CDL llid = 2745")

####

cdl_df <- as.data.frame(r, xy = TRUE) %>%
  dplyr::select(x, y, contains("2745"))
names(cdl_df)[3] <- "value"
cdl_df <- left_join(cdl_df, cdl_key, by = c("value" = "code")) 
cdl_df <- dplyr::filter(cdl_df, !is.na(category), 
                        category %in% test2$category)

g_raster <- ggplot() + 
  geom_raster(data = cdl_df, aes(x = x, y = y, fill = category)) +
  theme_void()

####

cowplot::plot_grid(g_raster, g_bar)
